Ellipsoids (v1.0): 3D Magnetic modelling of ellipsoidal bodies

### 2017-08-22 manuscript/manuscript.tex
change figure names for uploading the final files

%f
\begin{figure}[t]
\includegraphics[width=8.3cm]{figures/structural_orientation_angles.png}
\caption{Schematic representation of the coordinate systems used to
represent an ellipsoidal body.
(a) Main coordinate system with axes $x$, $y$, and $z$ pointing to
North, East, ans down, respectively.
The dark gray plane contains the centre $(x_{c}, y_{c}, z_{c})$
(white circle) and two unit vectors, $\mathbf{u}$ and $\mathbf{w}$, defining two
semi-axes of the ellipsoidal body. For triaxial and prolate ellipsoids,
$\mathbf{u}$ and $\mathbf{w}$ define, respectively,
the semi-axes $a$ and $b$. For oblate ellipsoids, $\mathbf{u}$ and
$\mathbf{w}$ define the semi-axes $b$ and $c$, respectively.
The strike direction is defined by the intersection of the
dark gray plane and the horizontal plane (represented in light gray),
which contains the $x$ and $y$ axes. The angle $\varepsilon$
between the $x$-axis and the strike direction is called \textit{strike}.
The angle $\zeta$ between the horizontal plane and the dark gray plane
is called \textit{dip}. The angle $\eta$ between the strike direction
and the line containing the unit vector $\mathbf{u}$
is called \textit{rake}. The projection of this line on the
horizontal plane (not shown) is called \textit{dip direction}
\citep{pollard2005, allmendinger2012}. (b) Local coordinate system
with origin at the ellipsoid centre $(x_{c}, y_{c}, z_{c})$
(black dot) and axes defined by unit vectors $\mathbf{v}_{1}$,
$\mathbf{v}_{2}$, and $\mathbf{v}_{3}$. These unit vectors
define the semi-axes $a$, $b$, and $c$ of triaxial, prolate,
and oblate ellipsoids in the same way.
For triaxial and prolate ellipsoids,
the unit vectors $\mathbf{u}$ and $\mathbf{w}$ shown in (a) coincide
with $\mathbf{v}_{1}$ and $\mathbf{v}_{2}$, respectively. For
oblate ellipsoids, the unit vectors $\mathbf{u}$ and $\mathbf{w}$
shown in (a) coincide with $\mathbf{v}_{2}$ and $\mathbf{v}_{3}$,
respectively.}
\label{fig:orientation-angles}
\end{figure}

%f
\begin{figure}[t]
\includegraphics[width=8.3cm]{figures/demag_factors.pdf}
\caption{(a) Comparison between the demagnetizing factors
$\tilde{n}^{\dagger}_{11}$ (in red),
$\tilde{n}^{\dagger}_{22}$ (in green), and
$\tilde{n}^{\dagger}_{33}$ (in blue)
produced by 100 triaxial ellipsoids with semi-axes
$a = a_{0} + u \; b_{0}$, $b = b_{0} + u \; b_{0}$, and
$c = c_{0} + u \; b_{0}$, where $0 \leq u \leq 10$ and
$b_{0} = 700$ \unit{m}.
The demagnetizing factors were calculated
by using Eqs. \ref{eq:n-tilde-dagger-11-triaxial},
\ref{eq:n-tilde-dagger-22-triaxial}, and \ref{eq:n-tilde-dagger-33-triaxial}.
(b) Comparison between the demagnetizing factors
$\tilde{n}^{\dagger}_{11}$ (in red) and
$\tilde{n}^{\dagger}_{22}$ (in green)
produced by 100 prolate ellipsoids with semi-axes
$a = m \; b_{0}$ and $b = b_{0}$, where $1.02 \leq m \leq 10$ and
$b_{0} = 1000$ \unit{m}.
The demagnetizing factors were calculated
by using Eqs. \ref{eq:n-tilde-dagger-11-prolate} and
\ref{eq:n-tilde-dagger-22-prolate}.
(c) Comparison between the demagnetizing factors
$\tilde{n}^{\dagger}_{11}$ (in red) and
$\tilde{n}^{\dagger}_{22}$ (in green)
produced by 100 oblate ellipsoids with semi-axes
$a = m \; b_{0}$ and $b = b_{0}$, where $0.02 \leq m \leq 0.98$ and
$b_{0} = 1000$ \unit{m}.
The demagnetizing factors were calculated
by using Eqs. \ref{eq:n-tilde-dagger-11-oblate} and
\ref{eq:n-tilde-dagger-22-oblate}.
The horizontal black line represent the value $1/3$.}
\label{fig:demag-factors}
\end{figure}

%f
\begin{figure}[t]
\includegraphics[width=8.3cm]{figures/confocal_ellipsoids_parallel_field.pdf}
\caption{Total-field anomaly (in \unit{nT}) produced by the 
synthetic bodies Ellipsoid 1 and Ellispoid 2, both
defined in Tab. \ref{tab:parameters-confocal-ellipsoids}.
The synthetic data produced by these confocal ellipsoids
were calculated on a regular grid of $200 \times 200$ points
at the constant vertical coordinate $z = 0$ \unit{m}.
These data were calculated with an uniform inducing field
parallel to the semi-axis $a$ of the confocal ellipsoids.}
\label{fig:tfa-confocal-ellipsoids-H0-parallel}
\end{figure}

%f
\begin{figure}[t]
\includegraphics[width=8.3cm]{figures/confocal_ellipsoids_oblique_field.pdf}
\caption{Total-field anomalies (in \unit{nT}) produced by the (a) Ellipsoid 1
and (b) Ellipsoid 2, both defined in Tab. \ref{tab:parameters-confocal-ellipsoids}.
The synthetic data produced by these confocal ellipsoids
were calculated on a regular grid of $200 \times 200$ points
at the constant vertical coordinate $z = 0$ \unit{m}.
These data were calculated with an uniform inducing field
which is oblique to the semi-axes of the confocal ellipsoids.
(c) Difference between the total-field anomalies shown in
b and a.}
\label{fig:tfa-confocal-ellipsoids-H0-oblique}
\end{figure}

%f
\begin{figure}[t]
\includegraphics[width=8.3cm]{figures/total-field_anomaly.pdf}
\caption{Total-field anomaly (in \unit{nT}) produced by the synthetic orebody
defined in Tab. \ref{tab:parameters-warrego}. The synthetic data
are calculated on a regular grid of $100 \times 100$ points
at the constant vertical coordinate $z = 0$ \unit{m}.}
\label{fig:tfa-warrego}
\end{figure}

%f
\begin{figure}[t]
\includegraphics[width=8.3cm]{figures/field_differences.pdf}
\caption{Difference between the total-field
anomaly calculated with the approximated magnetization $\breve{\mathbf{M}}$
(Eq. \ref{eq:M-approx}) and with the
true magnetization $\mathbf{M}$
(Eqs. \ref{eq:M-K-isotropic} and \ref{eq:M-K-isotropic-inverse-Lambda}).
The total-field anomalies are in \unit{nT} and were
calculated with Eq. \ref{eq:delta-T-approx},
on a regular grid of $100 \times 100$ points,
at the constant vertical coordinate $z = 0$ \unit{m}.
The differences are produced by the synthetic orebody defined in
Tab. \ref{tab:parameters-warrego}, but with different
isotropic susceptibilities:
(a) the isotropic susceptibility defined in
Tab. \ref{tab:parameters-warrego},
(b) an isotropic susceptibility $\chi = 0.1$ \unit{SI}, and
(c) an isotropic susceptibility $\chi = 0.116$ \unit{SI}.
This last value was calculated
with Eq. \ref{eq:chi-max}, by using $\epsilon = 8 \%$.}
\label{fig:tfa-differences-warrego}
\end{figure}

>>>>

%f
\begin{figure}[t]
\includegraphics[width=8.3cm]{figures/f01.png}
\caption{Schematic representation of the coordinate systems used to
represent an ellipsoidal body.
(a) Main coordinate system with axes $x$, $y$, and $z$ pointing to
North, East, ans down, respectively.
The dark gray plane contains the centre $(x_{c}, y_{c}, z_{c})$
(white circle) and two unit vectors, $\mathbf{u}$ and $\mathbf{w}$, defining two
semi-axes of the ellipsoidal body. For triaxial and prolate ellipsoids,
$\mathbf{u}$ and $\mathbf{w}$ define, respectively,
the semi-axes $a$ and $b$. For oblate ellipsoids, $\mathbf{u}$ and
$\mathbf{w}$ define the semi-axes $b$ and $c$, respectively.
The strike direction is defined by the intersection of the
dark gray plane and the horizontal plane (represented in light gray),
which contains the $x$ and $y$ axes. The angle $\varepsilon$
between the $x$-axis and the strike direction is called \textit{strike}.
The angle $\zeta$ between the horizontal plane and the dark gray plane
is called \textit{dip}. The angle $\eta$ between the strike direction
and the line containing the unit vector $\mathbf{u}$
is called \textit{rake}. The projection of this line on the
horizontal plane (not shown) is called \textit{dip direction}
\citep{pollard2005, allmendinger2012}. (b) Local coordinate system
with origin at the ellipsoid centre $(x_{c}, y_{c}, z_{c})$
(black dot) and axes defined by unit vectors $\mathbf{v}_{1}$,
$\mathbf{v}_{2}$, and $\mathbf{v}_{3}$. These unit vectors
define the semi-axes $a$, $b$, and $c$ of triaxial, prolate,
and oblate ellipsoids in the same way.
For triaxial and prolate ellipsoids,
the unit vectors $\mathbf{u}$ and $\mathbf{w}$ shown in (a) coincide
with $\mathbf{v}_{1}$ and $\mathbf{v}_{2}$, respectively. For
oblate ellipsoids, the unit vectors $\mathbf{u}$ and $\mathbf{w}$
shown in (a) coincide with $\mathbf{v}_{2}$ and $\mathbf{v}_{3}$,
respectively.}
\label{fig:orientation-angles}
\end{figure}

%f
\begin{figure}[t]
\includegraphics[width=8.3cm]{figures/f02.pdf}
\caption{(a) Comparison between the demagnetizing factors
$\tilde{n}^{\dagger}_{11}$ (in red),
$\tilde{n}^{\dagger}_{22}$ (in green), and
$\tilde{n}^{\dagger}_{33}$ (in blue)
produced by 100 triaxial ellipsoids with semi-axes
$a = a_{0} + u \; b_{0}$, $b = b_{0} + u \; b_{0}$, and
$c = c_{0} + u \; b_{0}$, where $0 \leq u \leq 10$ and
$b_{0} = 700$ \unit{m}.
The demagnetizing factors were calculated
by using Eqs. \ref{eq:n-tilde-dagger-11-triaxial},
\ref{eq:n-tilde-dagger-22-triaxial}, and \ref{eq:n-tilde-dagger-33-triaxial}.
(b) Comparison between the demagnetizing factors
$\tilde{n}^{\dagger}_{11}$ (in red) and
$\tilde{n}^{\dagger}_{22}$ (in green)
produced by 100 prolate ellipsoids with semi-axes
$a = m \; b_{0}$ and $b = b_{0}$, where $1.02 \leq m \leq 10$ and
$b_{0} = 1000$ \unit{m}.
The demagnetizing factors were calculated
by using Eqs. \ref{eq:n-tilde-dagger-11-prolate} and
\ref{eq:n-tilde-dagger-22-prolate}.
(c) Comparison between the demagnetizing factors
$\tilde{n}^{\dagger}_{11}$ (in red) and
$\tilde{n}^{\dagger}_{22}$ (in green)
produced by 100 oblate ellipsoids with semi-axes
$a = m \; b_{0}$ and $b = b_{0}$, where $0.02 \leq m \leq 0.98$ and
$b_{0} = 1000$ \unit{m}.
The demagnetizing factors were calculated
by using Eqs. \ref{eq:n-tilde-dagger-11-oblate} and
\ref{eq:n-tilde-dagger-22-oblate}.
The horizontal black line represent the value $1/3$.}
\label{fig:demag-factors}
\end{figure}

%f
\begin{figure}[t]
\includegraphics[width=8.3cm]{figures/f03.pdf}
\caption{Total-field anomaly (in \unit{nT}) produced by the 
synthetic bodies Ellipsoid 1 and Ellipsoid 2, both
defined in Tab. \ref{tab:parameters-confocal-ellipsoids}.
The synthetic data produced by these confocal ellipsoids
were calculated on a regular grid of $200 \times 200$ points
at the constant vertical coordinate $z = 0$ \unit{m}.
These data were calculated with an uniform inducing field
parallel to the semi-axis $a$ of the confocal ellipsoids.}
\label{fig:tfa-confocal-ellipsoids-H0-parallel}
\end{figure}

%f
\begin{figure}[t]
\includegraphics[width=8.3cm]{figures/f04.pdf}
\caption{Total-field anomalies (in \unit{nT}) produced by the (a) Ellipsoid 1
and (b) Ellipsoid 2, both defined in Tab. \ref{tab:parameters-confocal-ellipsoids}.
The synthetic data produced by these confocal ellipsoids
were calculated on a regular grid of $200 \times 200$ points
at the constant vertical coordinate $z = 0$ \unit{m}.
These data were calculated with an uniform inducing field
which is oblique to the semi-axes of the confocal ellipsoids.
(c) Difference between the total-field anomalies shown in
b and a.}
\label{fig:tfa-confocal-ellipsoids-H0-oblique}
\end{figure}

%f
\begin{figure}[t]
\includegraphics[width=8.3cm]{figures/f05.pdf}
\caption{Total-field anomaly (in \unit{nT}) produced by the synthetic orebody
defined in Tab. \ref{tab:parameters-warrego}. The synthetic data
are calculated on a regular grid of $100 \times 100$ points
at the constant vertical coordinate $z = 0$ \unit{m}.}
\label{fig:tfa-warrego}
\end{figure}

%f
\begin{figure}[t]
\includegraphics[width=8.3cm]{figures/f06.pdf}
\caption{Difference between the total-field
anomaly calculated with the approximated magnetization $\breve{\mathbf{M}}$
(Eq. \ref{eq:M-approx}) and with the
true magnetization $\mathbf{M}$
(Eqs. \ref{eq:M-K-isotropic} and \ref{eq:M-K-isotropic-inverse-Lambda}).
The total-field anomalies are in \unit{nT} and were
calculated with Eq. \ref{eq:delta-T-approx},
on a regular grid of $100 \times 100$ points,
at the constant vertical coordinate $z = 0$ \unit{m}.
The differences are produced by the synthetic orebody defined in
Tab. \ref{tab:parameters-warrego}, but with different
isotropic susceptibilities:
(a) the isotropic susceptibility defined in
Tab. \ref{tab:parameters-warrego},
(b) an isotropic susceptibility $\chi = 0.1$ \unit{SI}, and
(c) an isotropic susceptibility $\chi = 0.116$ \unit{SI}.
This last value was calculated
with Eq. \ref{eq:chi-max}, by using $\epsilon = 8 \%$.}
\label{fig:tfa-differences-warrego}
\end{figure}
